### 2021-03-17 paper.Rmd
brushing section draft

- Linked brushing (Earo)

> something from ggobi book

* Brushing as database query
* Brushing as conditioning
* Brushing as geometric sectioning
* Persistent vs. transient

> > figure 10: plots showing example

- Spin-and-brush  (Ursula)

>>>>

## Linked Brushing

Brushing is an interaction that results in a region being drawn onto the view of visualisation. When there are multiple views present the act of brushing can be thought of as a database query; points that fall inside the brush can be used as a lookup to highlight or filter data on adjacent views (Figure \ref{fig:brushing}). The effect of brushing can be transient, that is, the changes triggered by a brush are removed after use, or they can be persistent i.e. the changes to data within the same view or adjacent views remain (Figure \ref{fig:prim7-tour}). Brushing can be used to aid statistical and geometrical interpretations of the data; brushing can be thought of as conditioning variables on certain regions of the data or used to section lower dimensional views.

\begin{figure*}[!ht]
   \centering
         \includegraphics[width=0.45\textwidth]{figures/ggobi_book/brush_query.pdf}
         \includegraphics[width=0.45\textwidth]{figures/ggobi_book/brush_response.pdf}
\caption{When a user brushes data on the left panel, points that fall inside the region are highlighted in orange. The view on the right responds by higlighting the corresponding points.}
\label{fig:brushing}
\end{figure*}

## Spin-and-brush
